\input{Latex-Templates/packages}

\begin{document}
\section{Summary}
The Drunken Dragon is one of the most famous taverns of The Floating Lands, it's in Nova Spheris\footnote{Pop: 5 million people, Floating Pop: 500.000 people}, and it gathers many different kinds of people, and a whole lot of adventurers.
\section{Encounters}
\subsection{Planned Encounters}
First thing on the morning, before business resuming, a pair of drunks from the night before wake up, see each other and start shouting incoherent things to each other, in a really angry tone.

After dealing with that, make them notice that there not enough booze for the day. Remind them that they haven't seen the dwarf who gets them the booze in a while, so at least one of them goes to see her (Ingniss). The encounter is basically her trying to charge them more than normal for their usual deal.

At lunch make it so, some drunkards (half-orcs?) come after a morning of heavy drinking to drink and eat more (best if they still haven't gotten the booze from the dwarf). Make it so some customers leave immediately after them entering. And have them cause a lot ruckus, but no real damage. (If the party tries to make them leave, make it so the drunk call them racist, and actually argue decently that they haven't done anything that might make it so they should leave).


\subsection{Random Encounters}
\header{Random Encounter Table}
\begin{dndtable}[c p{6.7cm}]
    \textbf{1d10} & \textbf{Encounter}\\
    1-2 & A fake Health Inspector appears\\
    3 & A real Health Inspector appears\\
    4-6 & Roll on the Tavern Brawl Table\\
    7-8 & A Mysterious Patron appears\\
    9 & The city guard comes looking for someone\\
    10 & Re-roll twice, both happen in order
\end{dndtable}
\header{Tavern Brawl Table}
\begin{dndtable}[c p{6.7cm}]
    \textbf{1d12} & \textbf{Brawlers} \\
    1-4 & Drunk Half-Orcs (\dice{2d6+2})\\
    5-7 & Drunk Adventurers\\
    8-9 & Sober Adventurers\\
    10 & Racial Dispute\\
    11 & Failed robbery\\
    12 & Drunk Wizards (\dice{1d4+1})
\end{dndtable}
\header{Mysterious Patron Table}
\begin{dndtable}[c p{6.7cm}]
    \textbf{1d8} & \textbf{Patron}\\
    1-3 & Old wizard\\
    4-5 & Ancient metallic Dragon\\
    6 & Ancient chromatic Dragon\\
    7 & Werewolf\\
    8 & Deva
\end{dndtable}
\end{document}