\input{../../Latex-Templates/packages}

\begin{document}
\chapter{The Floating Lands}
\section{Summary}
The Floating Lands are a huge group of floating archipelagoes, moving through out the planes. It's home to several of the biggest cities on the realm, and a myriad of towns, with a diversity only a moving continent can have, it's normal to see every race imaginable, from humans to warforged.

\rowcolors{1}{statblockbg}{statblockbg}
\section{Information}

\begin{monsterbox}{Statistics}
    \textbf{Area:} 10 million \si{\square\kilo\meter}\\

    \textbf{Population:} 20 million\\

    \textbf{Races:}
    \begin{itemize}[leftmargin=1.3cm, labelsep=0.2cm]
        \item[40\%] Humans
        \item[15\%] Dwarves
        \item[10\%] Elves
        \item[5\%] Half-Elves
        \item[30\%]  Others
    \end{itemize}

    \textbf{Currency:}    Celestial Electrum/Silver/Copper   \\
\end{monsterbox}

\begin{monsterbox}{Useful statistics}
    \begin{itemize}[leftmargin=1.2cm, labelsep=0.2cm]
        \item[\textbf{Area:}] Islands go from big as continents to barely able to fit a town
        \item[\textbf{Pop:}] Varying settlement sizes, from metropolis to hamlets
        \item[\textbf{Races:}] All of them, mainly humans and humanoid species
    \end{itemize}
\end{monsterbox}


\section{Political Organization}
The vast majority of the nations are city-states which have control over the area around them\footnote{ranges from 0 to 100 kms. from their walls}

\section{Important Nations}
A brief summary of some important nations

\subsection{Imperos}
A former empire, named after the capital, and one of the only nations which has more than one city\footnote{Nova Spheris and The City of Iahu}. The current emperor, Giraldus the fourth, has recently taken the throne, after a bloody civil war, as such it's not clear what's gonna happen with them.

\subsection{The City of Aeria}
A city of magic, governed by the Council of the Five Sages, and home to the biggest and arguably the best magic academy in the realm. It's on the far end of the floating isles, in an unnaturally shaped island.

\subsection{New Helios}
A city dedicated to the Sun God, it's deeply religious and it's protected by the Helios Order (a Paladin Order). They claim to be the chosen people of the land, and while they seem LG, the ones in charge are LE and NE, clerics, which worship the true side of the Sun God.

\section{Main Cities and Towns}
A short list of cities and towns (ordered by population). This isn't all of them, and there are lots of nameless towns.
\subsection{Cities}
\begin{itemize}
    \item Imperos
    \item The City of Iahu
    \item New Helios
    \item The City of Aeria
    \item Nova Spheris
\end{itemize}
\subsection{Towns}
\begin{itemize}
    \item Nova Aurora
    \item Cloudhelm
    \item New Ethos
    \item Nova Halitos
    \item Zephyr
\end{itemize}

\end{document}